Flat-histogram method comparison on the 2D Ising model

### 2020-08-24 ising/ising-body.tex
added the necessary citation.

Because of the uncertainty of convergence for WL, many studies have been undertaken
to understand how the modification (or update) factor $\gamma$ impacts the
convergence~\cite{zhou2005understanding,lee2006convergence,
belardinelli2007wang}. Belardinelli and Pereyra showed that an update factor that decreases faster than $1/t$ leads to nonconvergence~\cite{belardinelli2007wang, belardinelli2008analysis, zhou2008optimal}, where $t$ corresponds to the number of moves. Schneider \emph{et al.} outline minor refinements algorithm including scaling the update factor with the number of energy bins~\cite{schneider2017convergence}.
These studies led to the
formation of the $1/t$-WL algorithm and have also led some researchers to follow
WL with a ``production run'' with fixed weights, in order to preserve ergodicity and
detailed balance~\cite{jayasri2005wang, mukhopadhyay2008monte}.
%
To our knowledge, this work is the first test of the convergence
properties of WL followed by a production run with comparison to other
methods.

>>>>

Because of the uncertainty of convergence for WL, many studies have been undertaken
to understand how the modification (or update) factor $\gamma$ impacts the
convergence~\cite{zhou2005understanding,lee2006convergence,
belardinelli2007wang}. Belardinelli and Pereyra showed that an update factor that decreases faster than $1/t$ leads to nonconvergence~\cite{belardinelli2007fast, belardinelli2007wang, belardinelli2008analysis, zhou2008optimal}, where $t$ corresponds to the number of moves. Schneider \emph{et al.} outline minor refinements algorithm including scaling the update factor with the number of energy bins~\cite{schneider2017convergence}.
These studies led to the
formation of the $1/t$-WL algorithm and have also led some researchers to follow
WL with a ``production run'' with fixed weights, in order to preserve ergodicity and
detailed balance~\cite{jayasri2005wang, mukhopadhyay2008monte}.
%
To our knowledge, this work is the first test of the convergence
properties of WL followed by a production run with comparison to other
methods.
